MSD panels 1, 2 and 3 HVE Supernatant

### 2016-10-17 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
Added summary statistics for IFNg concentrations.

HVE_all_panels_noStds <- HVE_all_panels_noStds%>%
  mutate(Estimated_Stock_Conc = ifelse(
    Sample_Dilution == "1:2", Calc..Concentration * 2,
    ifelse(Sample_Dilution == "1:5", Calc..Concentration *5, NA)
  ))

>>>>

HVE_all_panels_noStds <- HVE_all_panels_noStds%>%
  mutate(Estimated_Stock_Conc = ifelse(
    Sample_Dilution == "1:2", Calc..Concentration * 2,
    ifelse(Sample_Dilution == "1:5", Calc..Concentration *5, NA)
  ))
```

Apparently epithelial cells don't make IFNg, but we did get some signal. Here are the summary statistics for the dilution-corrected IFNg concentrations:

```{r check IFNg concentrations, echo=FALSE, message = FALSE, warning = FALSE}
##apparently epithelial cells aren't known to make IFNg, so let's check those concentrations

IFNgOnly<-HVE_all_panels_noStds %>%
  filter(Assay == "IFNg")

summary(IFNgOnly$Estimated_Stock_Conc)
